
\section{Prensenting the thesis}
\begin{itemize}
    \item Explain why I picked this approach
    \item Philosophy/thought process that lead to this approach
    \item What other approaches were considered and discarded? Why
    \item \emph{How did I know I was done?}
    \item \emph{When is the problem solved?}
    \item \emph{If you had to do it all over again would you do it differently?}
\end{itemize}

\begin{enumerate}
    \item Introduction
        \begin{itemize}
            \item Overall goal is to enable autonomous mapping and control about an asteroid using LIDAR
        \end{itemize}
    \item Mathematical background
        \begin{itemize}
            \item Three body dynamics
            \item Motion around an asteroid
            \item Polyhedron potential models
            \item Variational Integrators
            \item Geometric control
            \item Rigid body dynamics
        \end{itemize}
    \item Orbital transfers using reachability
    \item Geometric control for coupled motion
    \item Asteroid shape estimation and generation
    \item End-to-end mission examples
    \item Conclusions
        \begin{itemize}
            \item Areas for future research
        \end{itemize}
\end{enumerate}


\section{Each thesis chapter}
\begin{itemize}
    \item Introduction
        \begin{itemize}
            \item What is the chapter about?
            \item What sub-problem/issue is this chapter addressing?
            \item How does chapter fit within the overall story of the thesis?
        \end{itemize}
    \item The meat of the chapter
        \begin{itemize}
            \item Rigorous approach to the sub-problem or detailed explanation of issue
            \item Assumptions underlying this subproblem
            \item Validation: design, theory, implementation, graphs, figures
        \end{itemize}

    \item Summary
        \begin{itemize}
            \item Repeat the highlights of the chapter
            \item Transition to the next chapter. 
                How the chapter fits with the next one.
        \end{itemize}
\end{itemize}

\section{Summary/Slides}
\begin{itemize}
    \item Problem statement/hypothesis
    \item Why this is a hard/difficult problem?
    \item Approach/Methodology
    \item Why is this innovative/new?
    \item Assumptions/constraints?
    \item Initial results
    \item  Validation plan
    \item Limitations and applicability
    \item Expected contributions
    \item What's beyond  this thesis?
    \item Roadmap for the thesis
\end{itemize}

be able to answer the following questions
\begin{itemize}
    \item Why will work change the world?
    \item What would be done differently if I could start over?
    \item How will you know when success is reached?
    \item How much of the work can be generalized?
    \item Which part was research and which was engineering?
\end{itemize}
